%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Original author:
% Linux and Unix Users Group at Virginia Tech Wiki 
% (https://vtluug.org/wiki/Example_LaTeX_chem_lab_report)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[a4paper,11pt]{article}

\usepackage{graphicx} % Required for the inclusion of images
\usepackage{titling}

\setlength{\droptitle}{-13em}   % This is your set screw

\setlength\parindent{0pt} % Removes all indentation from paragraphs

\renewcommand{\labelenumi}{\alph{enumi}.} % Make numbering in the enumerate environment by letter rather than number (e.g. section 6)

\usepackage{times} % Uncomment to use the Times New Roman font

%----------------------------------------------------------------------------------------
%	DOCUMENT INFORMATION
%----------------------------------------------------------------------------------------

\title{SDP Group 8: Milestone 3 Individual Report} % Title

\author{Blake Hawkins} % Author name

\date{12 February, 2014} % Date of the milestone

\begin{document}

\maketitle % Insert the title, author and date

\begin{center}
Mentor: Katharina Heil % Instructor/supervisor
\\
Members: Blake Hawkins, % Partner names
Lubomir Vikev,
Borislav Ikonomov,
Yordan Stoyanov,
James Linehan,
Lukas Dirzys,
Iain Brown,
Emanuel Martinov,
Robaidh Mackinnon,
Aneesh Ghosh

\end{center}

%----------------------------------------------------------------------------------------
%	SECTION 1 (Contribution Summary)
%----------------------------------------------------------------------------------------

\section{Contribution Summary}

The first thing I did to the project was create an absolute boundary rectangle so that our convex hull calibration would (sometimes) ignore people standing immediately near the pitch. Throughout the week I did various documentation and refactoring improvements. I tested and fixed many regressions with our improved vision system. Next and most prominently I made some huge changes to the implementation of our m3defender class, using a new design pattern which would later be used officially. Many of the implemented functions were modular and would be used by the m3attacker and will be used for our real matches.
 
%----------------------------------------------------------------------------------------
%	SECTION 2 (High Points)
%----------------------------------------------------------------------------------------

\section{High Points}

\begin{itemize}
\item Testing and Regression fixes for new Vision system
\item Re-implementation of m3defender
\item Modular methods for simple tasks like "face point"
\end{itemize}

%----------------------------------------------------------------------------------------
%	SECTION 3 (Improvement Points)
%----------------------------------------------------------------------------------------

\section{Improvement Points}

\begin{itemize}
\item I would like to do more paired programming and code review directly with 1-2 other members at a time as I did for Milestone 2. This week felt very rushed but I'm also very happy with my performance.
\end{itemize}

%----------------------------------------------------------------------------------------
%	SECTION 4 (Self Assessment, Exceptional Contributions)
%----------------------------------------------------------------------------------------

\section{Self Assessment, Exceptional Contributions}

I would award myself a 7/10 due to the substantial amount of time I put into the vision system and defender methods this week. I feel that although I have some improvement points, this was also one of my most outstanding weeks.\\
\\
I would award a 9/10 to Yordan Stoyanov due to his work on a Vision refactoring which threaded our code, improving performance, and introduced logical control which improved the readability of our code overall. I would award 8/10 to Borislav Ikonomov for the time put into the m3attacker code, which he essentially finalized himself during the final days before the milestone.

%----------------------------------------------------------------------------------------
%	SECTION 6 (Extras, comment out to remove)
%----------------------------------------------------------------------------------------

% \section{Extra Comments}




\end{document}



