%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Original author:
% Linux and Unix Users Group at Virginia Tech Wiki 
% (https://vtluug.org/wiki/Example_LaTeX_chem_lab_report)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[a4paper,12pt]{article}

\usepackage{graphicx} % Required for the inclusion of images
\usepackage{titling}

\setlength{\droptitle}{-13em}   % This is your set screw

\setlength\parindent{0pt} % Removes all indentation from paragraphs

\renewcommand{\labelenumi}{\alph{enumi}.} % Make numbering in the enumerate environment by letter rather than number (e.g. section 6)

\usepackage{times} % Uncomment to use the Times New Roman font

%----------------------------------------------------------------------------------------
%	DOCUMENT INFORMATION
%----------------------------------------------------------------------------------------

\title{SDP Group 8: Milestone 2 Individual Report} % Title

\author{Blake Hawkins} % Author name

\date{5 February, 2014} % Date of the milestone

\begin{document}

\maketitle % Insert the title, author and date

\begin{center}
Mentor: Katharina Heil % Instructor/supervisor
\\
Members: Blake Hawkins, % Partner names
Lubomir Vikev,
Borislav Ikonomov,
Yordan Stoyanov,
James Linehan,
Lukas Dirzys,
Iain Brown,
Emanuel Martinov,
Robaidh Mackinnon,
Aneesh Ghosh

\end{center}

%----------------------------------------------------------------------------------------
%	SECTION 1 (Contribution Summary)
%----------------------------------------------------------------------------------------

\section{Contribution Summary}

I have spent the majority of the last week working on Vision code. My first accomplishment was recognising duplicate/dead code and improving the performance by refactoring or removing it. On Saturday Bobby and I had a long coding session in which I got the system to track all four robot plates simultaneously, along with the backbone for a simple orientation method, and extensive updates to the Vision documentation. Later I improved the orientation code and made it smooth. On Monday I spent a good chunk of time analysing the performance of different subsections, hence finding a bottleneck which I analysed further. I published my results in the documentation and refactored some more.
 
%----------------------------------------------------------------------------------------
%	SECTION 2 (High Points)
%----------------------------------------------------------------------------------------

\section{High Points}

\begin{itemize}
\item Cheap Orientation calculator
\item Major Documentation improvements for Vision
\item Useful performance analysis of Vision
\end{itemize}

%----------------------------------------------------------------------------------------
%	SECTION 3 (Improvement Points)
%----------------------------------------------------------------------------------------

\section{Improvement Points}

\begin{itemize}
\item None. I felt that I made good progress on my previous week's improvement points.
\end{itemize}

%----------------------------------------------------------------------------------------
%	SECTION 4 (Self Assessment, Exceptional Contributions)
%----------------------------------------------------------------------------------------

\section{Self Assessment, Exceptional Contributions}

I would award myself a 3.5/5, because I spent a large amount of time working in pairs and discussing points of interest with my team, as well as making major useful contributions to the codebase.\\
\\
I would award a 4/5 to both Lubomir Vikev and James Linehan, due to their implementation as a pair of a pneumatic kicker, which is arguably outstanding and unique work in SDP. Additionally, Lubo has run into major issues with his Trac server, which he fixed by himself in a matter of days.

%----------------------------------------------------------------------------------------
%	SECTION 6 (Extras, comment out to remove)
%----------------------------------------------------------------------------------------

% \section{Extra Comments}




\end{document}



